Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-30 review_article.Rmd
add links for all maps to figure caption

```{r choropleth-grid-create, message=FALSE, fig.cap = "Public facing choropleth cancer maps. [Globocan 2012: Estimated  Cancer Incidence, Mortality and Prevalence](http://globocan.iarc.fr/Pages/Map.aspx), "}
library(grid)
library(png)
library(gridExtra)

>>>>

```{r choropleth-grid-create, message=FALSE, fig.cap = "Public facing choropleth cancer maps. From right to left and top to bottom: [a. Globocan 2012: Estimated  Cancer Incidence, Mortality and Prevalence](http://globocan.iarc.fr/Pages/Map.aspx)  (Incidence rates per 100,000 for all cancers, male and female),  [b. Bowel Cancer Australia Atlas](http://www.bowelcanceratlas.org/), [c. Atlas of Cancer in QLD - Relative incidence ration, Lung cancer in males](https://cancerqld.org.au/research/queensland-cancer-statistics/queensland-cancer-atlas/), [d. CINA+ Online Cancer in North America](http://www.cancer-rates.info/naaccr/) (Incidence rates of all invasive cancers per 100,000, male and female), [e. Atlas of Childhood Cancer in Ontario](http://www.pogo.ca/research-data/pogo-atlas/) (Incidence rate of childhood cancer per 100,000, men and women), [f. An Atlas of Cancer in South Australia](https://www.cancersa.org.au/assets/images/pdfs/An%20Atlas%20of%20Cancer%20in%20South%20Australia%20-%20Full%20Report.pdf) (Incidence rate per 100,00, lung cancer in females), [g. The Environment and Health Atlas of England and Wales](http://www.envhealthatlas.co.uk/eha/Breast/) (Lung cancer in females), [h. Map of Cancer Mortality Rates in Spain](http://elpais.com/elpais/2014/10/06/media/1412612722_141933.html) (Relative risk, Lung cancer, men vs women), [i. United States Cancer Statistics: An Interactive Cancer Statistics Website](https://nccd.cdc.gov/DCPC_INCA/) (Incidence rate per 100,000, all cancer types, men and women"}

library(grid)
library(png)
library(gridExtra)
